### 2016-06-09 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Minor changes to uncertainty section of gas burner report

\subsubsection{Thermocouples}
The standard uncertainty in the temperature of the thermocouple wire itself is $\pm$2.2$~^{\circ}$C at $277~^{\circ}$C and increases to $\pm$9.5$~^{\circ}$C at $871~^{\circ}$C as determined by the wire manufacturer~\cite{Omega:2004}. The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty~\cite{Pitts:2003}. Blevins found the maximum percent error for the upper layer temperature measured by a 1~mm bare-bead thermocouple to be 20~\%~\cite{Blevins:1999}. Small diameter thermocouples were used during these experiments to limit the impact of radiative heating and cooling. The estimated total expanded uncertainty for temperature in these experiments is $\pm$15~\%.

@@

\begin{table}[!ht]
\caption{Heat Release Rates for East Structure Tests}
\begin{tabular}{lccccc}
 \toprule
 					& 	\multicolumn{5}{c}{\textbf{Heat Release Rate (kW)}} \\
\textbf{Test} 		&	\begin{tabular}{c} Corner \\ Burner On \end{tabular} 
					&	\begin{tabular}{c} Middle \\ Burner On \end{tabular}
					&	\begin{tabular}{c} Center \\ Burner On \end{tabular}
					& 	\begin{tabular}{c} Center \\ Burner Off \end{tabular}
					&   \begin{tabular}{c} Middle \\ Burner Off \end{tabular} \\
 \midrule
% Original Values
% Test 2 				& 338 & 651	& 901 & 634 & 330 \\
% Test 3 				& 326 & 650	& 905 & 631 & 326 \\
% Test 4				& 351 & 654	& 952 & 652 & 337 \\
% Rounded Values
Test 2 				& 340 & 650	& 900 & 630 & 330 \\
Test 3 				& 330 & 650	& 910 & 630 & 330 \\
Test 4				& 350 & 650	& 950 & 650 & 337 \\
\midrule
 & \multicolumn{2}{c}{\textbf{Heat Release Rate (kW)}} & \multicolumn{3}{c}{} \\
\textbf{Test} 		& \multicolumn{2}{c}{All Burners On} 
& \multicolumn{3}{c}{} \\
\midrule
% Original Values
% Test 5 - Seq. 1		& \multicolumn{2}{c}{725} & \multicolumn{3}{c}{} \\
% Test 5 - Seq. 2		& \multicolumn{2}{c}{728} & \multicolumn{3}{c}{} \\
% Test 5 - Seq. 3		& \multicolumn{2}{c}{723} & \multicolumn{3}{c}{} \\
% Test 6 - Seq. 1		& \multicolumn{2}{c}{722} & \multicolumn{3}{c}{} \\
% Test 6 - Seq. 2		& \multicolumn{2}{c}{721} & \multicolumn{3}{c}{} \\
% Test 6 - Seq. 3		& \multicolumn{2}{c}{714} & \multicolumn{3}{c}{} \\
% Rounded Values
Test 5 - Seq. 1		& \multicolumn{2}{c}{730} & \multicolumn{3}{c}{} \\
Test 5 - Seq. 2		& \multicolumn{2}{c}{730} & \multicolumn{3}{c}{} \\
Test 5 - Seq. 3		& \multicolumn{2}{c}{720} & \multicolumn{3}{c}{} \\
Test 6 - Seq. 1		& \multicolumn{2}{c}{720} & \multicolumn{3}{c}{} \\
Test 6 - Seq. 2		& \multicolumn{2}{c}{720} & \multicolumn{3}{c}{} \\
Test 6 - Seq. 3		& \multicolumn{2}{c}{710} & \multicolumn{3}{c}{} \\
\bottomrule
\end{tabular}
\label{table:HRR_East}
\end{table}

@@

\begin{table}[!ht]
\caption{Heat Release Rates for West Structure Tests}
\begin{tabular}{lc}
 \toprule
					& 	\textbf{Heat Release Rate (kW)}	\\
\textbf{Test}		& All burners on \\
 \midrule
% Original Values
% Test 22				&     	764 	  \\
% Test 23				&     	789 	  \\
% Test 24				& 	    789 	  \\
% Test 25				&     	786 	  \\
% Rounded Values
Test 22				&     	760 	  \\
Test 23				&     	790 	  \\
Test 24				& 	    790 	  \\
Test 25				&     	790 	  \\
\bottomrule
\end{tabular}
\label{table:HRR_West}
\end{table}

>>>>

\subsubsection{Thermocouples}
The standard uncertainty in the temperature of the thermocouple wire itself is $\pm$2.2$~^{\circ}$C at $277~^{\circ}$C and increases to $\pm$9.5$~^{\circ}$C at $871~^{\circ}$C as determined by the wire manufacturer~\cite{Omega:2004}. The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty. Maximum percent error has been reported to be as high as 20~\% for upper layer temperatures measured by a 1~mm bare-bead type K thermocouple~\cite{Blevins:1999,Pitts:2003}. Small diameter thermocouples were used during these experiments to limit the impact of radiative heating and cooling. The estimated total expanded uncertainty for temperature in these experiments is $\pm$15~\%.

@@

\begin{table}[!ht]
\caption{Heat Release Rates for East Structure Tests}
\begin{tabular}{lccccc}
 \toprule
 					& 	\multicolumn{5}{c}{\textbf{Heat Release Rate (kW)}} \\
\textbf{Test} 		&	\begin{tabular}{c} Corner \\ Burner On \end{tabular} 
					&	\begin{tabular}{c} Middle \\ Burner On \end{tabular}
					&	\begin{tabular}{c} Center \\ Burner On \end{tabular}
					& 	\begin{tabular}{c} Center \\ Burner Off \end{tabular}
					&   \begin{tabular}{c} Middle \\ Burner Off \end{tabular} \\
 \midrule
Test 2 				& 340 & 650	& 900 & 630 & 330 \\
Test 3 				& 330 & 650	& 910 & 630 & 330 \\
Test 4				& 350 & 650	& 950 & 650 & 340 \\
\midrule
 & \multicolumn{2}{c}{\textbf{Heat Release Rate (kW)}} & \multicolumn{3}{c}{} \\
\textbf{Test} 		& \multicolumn{2}{c}{All Burners On} 
& \multicolumn{3}{c}{} \\
\midrule
Test 5 - Seq. 1		& \multicolumn{2}{c}{730} & \multicolumn{3}{c}{} \\
Test 5 - Seq. 2		& \multicolumn{2}{c}{730} & \multicolumn{3}{c}{} \\
Test 5 - Seq. 3		& \multicolumn{2}{c}{720} & \multicolumn{3}{c}{} \\
Test 6 - Seq. 1		& \multicolumn{2}{c}{720} & \multicolumn{3}{c}{} \\
Test 6 - Seq. 2		& \multicolumn{2}{c}{720} & \multicolumn{3}{c}{} \\
Test 6 - Seq. 3		& \multicolumn{2}{c}{710} & \multicolumn{3}{c}{} \\
\bottomrule
\end{tabular}
\label{table:HRR_East}
\end{table}

@@

\begin{table}[!ht]
\caption{Heat Release Rates for West Structure Tests}
\begin{tabular}{lc}
 \toprule
					& 	\textbf{Heat Release Rate (kW)}	\\
\textbf{Test}		& All burners on \\
 \midrule
Test 22				&     	760 	  \\
Test 23				&     	790 	  \\
Test 24				& 	    790 	  \\
Test 25				&     	790 	  \\
\bottomrule
\end{tabular}
\label{table:HRR_West}
\end{table}
